An Image-based method for phase estimation, gating and temporal super-resolution of \\cardiac ultrasound

### 2017-02-16 paper155.tex
Updated figure properties, combined simMat images, combined phase ordered images

@@

\includegraphics[width=1.5in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/simMat.png}
\includegraphics[width=1.5in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/simMat_Trend.png}
\includegraphics[width=1.5in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/simMat_Seasonal.png}
\ionbox{1.5in}\ionbox{1.5in}\ionbox{1.5in}\\
\includegraphics[width=4.5in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/season_trend_decomposition.png}
\ionbox{4.5in}
\includegraphics[width=4.5in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/instantaneous_phase.png}
\ionbox{4.5in}
\subsection{Gating of respiratory frames}
\label{sec:method:gating}

%
%\vspace{-0.5cm}
\subsection{Reconstruction of one-period video at high temporal resolution}
\label{sec:method:super_resolution}
%

%\vspace{-0.5cm}
\section{Results}
\label{sec:results}
%

%
%\vspace{-0.5cm}
\section{Discussion and future work}
\label{sec:discussion}
%

>>>>

\includegraphics[width=4.75in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/simMat.png}
\ionbox{4.75in}\\
\includegraphics[width=4.75in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/season_trend_decomposition.png}
\ionbox{4.75in}\\
\includegraphics[width=4.75in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/periodogram.png}
\ionbox{4.75in}\\
\includegraphics[width=4.75in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/instantaneous_phase.png}
\ionbox{4.75in}\\

@@

%\vspace{-0.5cm}
\subsection{Gating of respiratory frames}
\label{sec:method:gating}
%

%
\begin{IonFigT}
\centering
%
\includegraphics[width=5.0in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/respiratory_phase_gating.png}
\ionbox{5.0in}\\
\includegraphics[width=5.0in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/robust_lowess_gating.png}
\ionbox{5.0in}\\
%
\caption{Illustration of our method for gating respiratory frames}
\label{fig:respiratory_gating}
\end{IonFigT}
%
%\vspace{-0.5cm}
\subsection{Reconstruction of one-period video at high temporal resolution}
\label{sec:method:super_resolution}
%

%\vspace{-0.5cm}
\section{Results}
\label{sec:results}
%
%
\begin{IonFigT}
\centering
%
\includegraphics[width=5.0in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/phaseordered.png}
\ionbox{5.0in}\\
%
\caption{Visualization of video frames are ordered by estimated cardiac phase}
\label{fig:phase_ordering}
\end{IonFigT}
%
%
%\vspace{-0.5cm}
\section{Discussion and future work}
\label{sec:discussion}
%
